A new type of generic, self-evolving and efficient automated deduction algorithm based on category theory

### 2023-04-25 Math-7081.tex
copy downloaded file~

\begin{document}
	\title{A new type of generalized, self-evolving and efficient automated deduction algorithm based on category theory}
	\author{%
		Shao Xinhui\affil{1}\corrauth
		Zijian Wang\affil{2}
	}
	\shortauthors{the Authors}
	\address{%
		\addr{\affilnum{1}}{Department of Mathematics, College of Sciences, Northerneastern University, Shenyang, Liaoning, P.R.China}
		\addr{\affilnum{2}}{Northeast Yucai School, Zhenxing St. 9-5, Heping District, Shenyang, Liaoning, P.R.China}
		\corraddr{shaoxinhui@mail.neu.edu.cn}
	}

@@

@@

	\section*{Conflict of interests}
	This research did not receive any specific grant from funding agencies in the public, commercial, or
	not-for-profit sectors.

>>>>

\begin{document}
	\title{A new type of generic, self-evolving and efficient automated deduction algorithm based on category theory}
	\author{%
		Zijian Wang\affil{1}
		Shao Xinhui\affil{*}
	}
	\shortauthors{the Authors}
	\address{%
		\addr{\affilnum{1}}{Northeast Yucai School, Zhenxing St. 9-5, Heping District, Shenyang, Liaoning, P.R.China. Email: felix\_wzj@yahoo.com}
		\corraddr{Department of Mathematics, College of Sciences, Northerneastern University, Shenyang, Liaoning, P.R.China. Email: shaoxinhui@mail.neu.edu.cn}
	}

@@

	\section{Testing the algorithm's performance through benchmarks}

	The discussion below is based on an implementation of the algorithm by us, called DefQed and is open-sourced on \cite{Wang2022}. It will be further described in the sixth section.

	To illustrate the performance of the brand-new algorithm, we construct a relatively simple exemplification. The source code describing the demonstration can be found on the internet through \cite{Wang2022-2}. The code for Wolfram Engine (or Wolfram Mathematica) is also presented.

	The timing cost by the three provers are shown as below in \ref{table-2}.

	\begin{table}[h]
		\centering
		\caption{Timing (ms) of the three algorithms.}
		\begin{tabular}{ccc}
			\toprule
			Round$\sharp$ & DefQed & Wolfram Engine \\
			\midrule
			1 & 576 & 141  \\ 
			2 & 727 & 250  \\ 
			3 & 752 & 375  \\ 
			4 & 889 & 266  \\ 
			\bottomrule
		\end{tabular}
		\label{table-2}
	\end{table}

	The data can be further illustrated in \ref{figure-4}. The blue line stands for the time (milliseconds) of DefQed, while the orange line stands for the time (milliseconds) of Wolfram Engine.

	\begin{figure}[h]
		\centering
		\includegraphics{plot.eps}
		\caption{The plots of the data measures.}
		\label{figure-4}
	\end{figure}

	From \ref{figure-4} we can obviously tell the time cost of the reasoning increases by the round, as more reflections are inserted into the database. It should be noted that for time reasons, the reduction algorithm is not implemented in this version of DefQed, and the coding quality can also be further improved.

	The experiment is done on a Hewlett-Packard ZBook mobile workstation 14u G5 \cite{HP-2018}. During the experiment, all the programs/applications not necessary are closed except for the terminal emulator (ConEmu) and the program to benchmark. The operating system is Microsoft Windows 11 Pro for Workstations Insider Preview (Build 25211). The processor is Intel Core i5 8250U and the memory size is 8.0 GB installed. We used Wolfram Language version 12.0 and DefQed version 0.03. As DefQed utilizes MySQL as its database, it is necessary to point out we are using MySQL version 8.0 (Community). The DefQed source code is built with option `Release Mode' for Microsoft Windows x64 processor with .NET 6.0 platform.

	We also need to point out that though in each round DefQed seems to be slower than others, it does not mean that the algorithm has a worse efficiency and performance when comparing to others. The performance difference between platform and programming language utilized by the two, .NET and mainly C contributes to the difference of the two applications, not mentioning that while Wolfram Engine can only prove equations, DefQed is a generic approach. The quality of the optimization of the codes are also not on be same basis.

@@

	\section*{Conflict of interests}
	This research did not receive any specific grant from funding agencies commercially. However, it does receive general aid from the Yingcai Project of P.R.China.
